---
title: "Assignment 2 - Data Products Course"
author: "jbassard"
date: "August 12 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Synopsis
This is the second project assignment for the Developping Data Products course in Coursera's Data Science specialization track. **The purpose of this project is to create an interactive plot with plotly R package.** I will create an interactive plot with the data of the artisanal companies in France (numbers, sales revenue, net added value) per department. Original Data is downloaded from data.gouv.fr.


### Checking for required packages and install them if necessary, then load them
```{r}
if (!require("plotly")) {
	 install.packages("plotly")}
if (!require("readxl")) {
	 install.packages("readxl")}
library(plotly)
library(readxl)
```

## Loading data
### Downloading data in DataProduct folder
```{r, eval=FALSE}
if(!file.exists("./DataProduct2")) {
	dir.create("./DataProduct2")}
if(!file.exists("./DataProduct2/artisans_etalab.xls")) {
	fileUrl1 <- "https://www.data.gouv.fr/storage/f/2014-01-13T18-09-10/artisans_etalab.xls"
	download.file(fileUrl1, destfile="./DataProduct2/artisans_etalab.xls")}
```

### Loading the data
```{r}
Artisan <- read_xls("./DataProduct2/artisans_etalab.xls")
```

## Quick Exploration of the dataset
```{r}
dim(Artisan)
head(Artisan)
str(Artisan)
```

## The interactive plot

```{r}
plot_ly(data = Artisan) %>%
  add_trace(x = ~Departement, y = ~entreprises_artisanales, type = "bar", color = I("green"), name = "Artisanal Company Numbers") %>%
  add_trace(x = ~Departement, y = ~chiffre_affaires, yaxis = "y2", type = "bar", color = I("blue"), name = "Sales Revenue in Euros") %>%
  add_trace(x = ~Departement, y = ~Valeur_ajoutee, yaxis = "y2", type = "bar", color = I("purple"), name = "Net Added Value in Euros") %>%
  layout(title = "the artisanal companies in France per department", yaxis2 = list(overlaying = "y2", side = "right"), yaxis = list(title = FALSE), xaxis = list(title = FALSE))

```
```